Revisiting the hydrodynamic wave modulation from linear wave theory

### 2024-06-24 paper/paper.tex
Fix syntax and color range in modulation 3-panels
Comparing analytical and numerical solutions

\subsection{Wavenumber and amplitude modulation}
\label{subsection:analytical_solutions}

@@

@@

To determine $\widetilde{\g}$, we will need to evaluate the modulation of
the gravitational acceleration at the surface of the long wave.

\begin{equation}
\label{eq:eta_stokes}
\eta_{St} = a_L \left[
  \cos{\psi} +
  \dfrac{1}{2} \varepsilon_L \cos{2\psi} +
  \varepsilon_L^2 \left( \dfrac{3}{8} \cos{3\psi} - \dfrac{1}{16} \cos{\psi} \right)
\right]
\end{equation}

The corresponding gravitational acceleration at the surface of the Stokes wave
is:

\subsection{Lagrangian averaged short-wave properties}

Stokes drift is a residual Lagrangian drift that occurs due to the wave orbits
not being closed under a propagating wave
\cite{stokes1847,kenyon1969stokes,van2018stokes}:

\begin{equation}
\label{}
u_s = a^2 \omega k e^{2kz}
\end{equation}
for a monochromatic wave in deep water.
Stokes drift has been successfully used to predict material transport on the
ocean surface \cite{rohrs2012observation,curcic2016hurricane}.
It can be derived from linear wave theory by integrating the wave orbital
velocity following material orbits \cite{phillips1966dynamics}:

\begin{equation}
\label{eq:lagrangian_average}
u_s = \overline{
  u(\psi) + 
  \zeta \dfrac{\partial u}{\partial x} +
  \xi \dfrac{\partial w}{\partial z}
}
\end{equation}
where $\zeta$ and $\xi$ are horizontal and vertical excursions of the orbits,
respectively.

To obtain an average modulation of the short-wave properties, we apply the same
Lagrangian integration approach used to obtain Stokes drift.

\begin{equation}
\label{eq:stokes_wavenumber}
\widetilde{k_s} = \overline{
  \widetilde{k}(\psi) +
  \zeta \dfrac{\partial \widetilde{k}}{\partial x} +
  \xi \dfrac{\partial \widetilde{k}}{\partial z}
}
= k \left( 1 + a_L^2 k_L^2 \right)
\end{equation}

\begin{equation}
\label{eq:stokes_gravity}
\widetilde{g_s} = \overline{
  \widetilde{g}(\psi) +
  \zeta \dfrac{\partial \widetilde{g}}{\partial x} +
  \xi \dfrac{\partial \widetilde{g}}{\partial z}
}
= g \left( 1 + \dfrac{3}{2} a_L^2 k_L^2 \right)
\end{equation}

>>>>

\subsection{Wavenumber modulation}
\label{subsection:wavenumber_modulation}

@@

\begin{equation}
\label{eq:eta_stokes}
\eta_{St} = a_L \left[
  \cos{\psi} +
  \dfrac{1}{2} \varepsilon_L \cos{2\psi} +
  \varepsilon_L^2 \left( \dfrac{3}{8} \cos{3\psi} - \dfrac{1}{16} \cos{\psi} \right)
\right]
\end{equation}
The corresponding gravitational acceleration at the surface of the Stokes wave
is, to the 4$^{th}$ order:

\subsection{Amplitude and steepness modulation}
\label{subsection:amplitude_modulation}

@@
